% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Swetha Raja}
\newcommand{\CVTitle}{Swetha Raja's CV for DDS Applications}
\newcommand{\CVNote}{CV compiled on {\today} for DDS Applications}
\newcommand{\CVWebpage}{https://in.linkedin.com/in/swetha-raja-48a65a12a}
\newcommand{\uLouisville}{\href{http://louisville.edu/dentistry}
{\textbf{University of Louisville}},
Louisville, Kentucky, USA}
\newcommand{\ramachandra}{\href{http://www.sriramachandra.edu.in/}
{\textbf{Sri Ramachandra Dental College and Hospital}},
Chennai, Tamil Nadu, India}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.com/maps/place/2234+S+Preston+St,+Louisville,+KY+40217}
{2234 S. Preston St Apt 4, Louisville, Kentucky 40217, USA}
\par
\href{mailto:swetharaja5593@gmail.com}
{swetharaja5593@gmail.com}
\,\SubBulletSymbol\,
+1\,(513)\,394-0377
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\uLouisville

\Gap
\BulletItem
Masters in
\href{https://louisville.edu/dentistry/sandelllab}
{Oral Biology}
\textit{(In Progress)}
\hfill
\DatestampYMD{2016}{01}{16} --
\DatestampYMD{2017}{12}{31}
\begin{Detail}
\SubBulletItem
Thesis:
Mechanisms Underlying Retinoic Acid Deficient Cleft of the Secondary Palate
\SubBulletItem
Adviser:
Dr.~Lisa~Sandell
\SubBulletItem
Cumulative GPA: 3.79 / 4.0
\end{Detail}

\BigGap
\Entry
\href{http://www.sriramachandra.edu.in/}
{\textbf{Sri Ramachandra Dental College and Hospital}},
Chennai, Tamil Nadu, India

\Gap
\BulletItem
Bachelor of
\href{http://www.sriramachandra.edu.in/university/dci}
{Dental Surgery}
\hfill
\DatestampYMD{2010}{07}{08} --
\DatestampYMD{2015}{07}{15}
\begin{Detail}
\SubBulletItem
Graduated with College Honors.
\SubBulletItem
Cumulative GPA: 3.96 / 4.00
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% CLINICAL EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%
\Section
{Clinical Experience}
{Clinical Experience}
{PDF:ClinicalExperience}

\Entry
\href{http://mortensondental.com/}
{\textbf{Mortensons Family Dental}},
Louisville, Kentucky, USA

\Gap
\BulletItem
Dental Observership/Shadowing
\hfill
\DatestampYMD{2015}{05}{08} --
Present
\begin{Detail}
\SubBulletItem
Employer:
Dr. Robert Fuchs
\SubBulletItem
Hours~shadowed: 
\textbf{320~hours}\textit{~and~counting}
\end{Detail}


\BigGap
\Entry
\href{http://www.sriramachandra.edu.in/}
{\textbf{Sri Ramachandra Dental College and Hospital}},
Chennai, Tamil Nadu, India

\Gap
\BulletItem
Internship
\hfill
\DatestampYMD{2014}{07}{08} --
\DatestampYMD{2015}{07}{08}
\begin{Detail}
\SubBulletItem
Rotations:
Dept. of Endodontics, Public Health Dentistry, Pediatric Dentistry, Periodontics, Oral surgery, Oral Medicine, Oral Pathology, Orthodontics  
\SubBulletItem
Hours~worked: 
\textbf{2400 hours}
\end{Detail}


\BigGap
\Entry
\href{http://www.smilesindia.com/}
{\textbf{Smiles India Family Dentistry}},
Chennai, Tamil Nadu, India

\Gap
\BulletItem
Associate Dental Surgeon
\hfill
\DatestampYMD{2014}{08}{08} --
\DatestampYMD{2015}{11}{08}
\begin{Detail}
\SubBulletItem
Employer:
Dr.~Arunachalam
\SubBulletItem
Hours~worked: 
\textbf{1200 hours}
\end{Detail}

\BigGap
\Entry
\href{http://www.dent.umich.edu}
{\textbf{University of Michigan}},
Ann Arbor, Michigan, USA

\Gap
\BulletItem
Dental Observership/Shadowing
\hfill
\DatestampYMD{2016}{03}{08}
\begin{Detail}
\SubBulletItem
Employer:
\href{http://www.dent.umich.edu/about-school/department/opd/graduate-program-orthodontics}
{\textbf{Dept. of Orthodontics and Pediatric Dentistry}}
\SubBulletItem
Hours~shadowed: 
\textbf{32 hours}
\end{Detail}


\BigGap
\Entry
\href{http://www.dent.umich.edu}
{\textbf{University of Louisville}},
Louisville, Kentucky, USA

\Gap
\BulletItem
Dental Observership/Shadowing
\hfill
\DatestampYMD{2016}{04}{08}
\begin{Detail}
\SubBulletItem
Employer:
\href{http://louisville.edu/dentistry}
{\textbf{Dept. of Pediatric Dentistry}}
\SubBulletItem
Hours~shadowed: 
\textbf{10 hours}
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\Entry
\uLouisville

\Gap
\BulletItem
Summer Research Fellow, Dept. Of Molecular, Cellular \& Craniofacial Biology
\hfill 
\DatestampYMD{2016}{05}{08} --
\DatestampYMD{2016}{08}{08}
\begin{Detail}
\SubBulletItem
Project:
Mechanisms Underlying Retinoic Acid Deficient Cleft of the Secondary Palate
\SubBulletItem
Supervisor:
Dr.~Lisa~Sandell
\end{Detail}

\BigGap
\Entry
\href{http://www.sriramachandra.edu.in/university/dci}
{\textbf{Sri Ramachandra Dental College and Hospital}},


\Gap
\BulletItem
Summer Research Fellow, Dept. of Endodontics
\hfill
\DatestampYMD{2015}{05}{08} --
\DatestampYMD{2015}{08}{15}
\begin{Detail}
\SubBulletItem
Project:
Evaluation of Shear Bond Strength of Anti-Bacterial Property Containing Bonding Agent
\SubBulletItem
Supervisor:
Dr.~Kandaswamy
\end{Detail}

\Gap
\BulletItem
Summer Research Fellow, Dept. of Public Health Dentistry
\hfill
\DatestampYMD{2015}{05}{08} --
\DatestampYMD{2015}{08}{15}
\begin{Detail}
\SubBulletItem
Project:
Microbiological Evaluation of Toothbrush Bristles with and without a Protective Cover-An in-vitro study
\SubBulletItem
Supervisor:
Dr.~Raj~Kumar~Manoharan
\end{Detail}

\Gap
\BulletItem
Student Clinician, Dept. of Orthodontics
\hfill
\DatestampYMD{2013}{12}{08} --
\DatestampYMD{2014}{02}{15}
\begin{Detail}
\SubBulletItem
Project:
Tr(Y) innovation - a Bracket with a Change
\SubBulletItem
Supervisor:
Dr.~Vignesh~Kailasam
\SubBulletItem
Collaborated with the \textbf{Mechanical Engineering Dept., Indian Institute of Technology} and designed an orthodontic bracket that could exhibit three different torque values. Presented this at the \textbf{$18^{th}$ Dentsply Student Clinician Research Program} and was awarded the second runner up.
\end{Detail}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
Tuition Scholarship Award, Graduate Program in Oral Biology
\hfill
\DatestampY{2016}
\begin{Detail}
\Item
Received a scholarship amount of \$4000  during Spring 2016 and \$2500  during Summer 2016 for good academic standing.
\end{Detail}

\BulletItem
International Student Tuition Scholarship Award
\hfill
\DatestampY{2016}
\begin{Detail}
\Item
One of the 10 awardees who received a scholarship amount of \$500  during Fall 2016. 
\end{Detail}

\Gap
\BulletItem
Gold Medallist, Best Out-Going Student,
Sri Ramachandra Dental College and Hospital
\hfill
\DatestampY{2015} 
\begin{Detail}
\Item
For outstanding performance during Undergraduate Dental Studies.
\end{Detail}

\Gap
\BulletItem
IDA-Colgate Scholarship Award,
Sri Ramachandra Dental College and Hospital
\hfill
\DatestampY{2010} --
\DatestampY{2014}
\begin{Detail}
\Item
For standing first in class during first through third year and second in final year of dental studies.
\end{Detail}

\Gap
\BulletItem
Gold Medallist,
{Indian Association of Oral Medicine and Radiology}
\hfill
\DatestampY{2014}
\begin{Detail}
\Item
For outstanding performance in Oral Medicine and Radiology during undergraduate studies.
\end{Detail}

\Gap
\BulletItem
Gold Medallist,
Tamil Nadu Association of Anatomist
\hfill
\DatestampY{2012}
\begin{Detail}
\Item
For outstanding performance in Anatomy during undergraduate studies.
\end{Detail}

%%%%%%%%%%%%%%%%%%%
%% PRESENTATIONS %%
%%%%%%%%%%%%%%%%%%%
\Section{Presentations}{Presentations}{Presentations}

\Entry
\textbf{Research! Louisville}
\BulletItem
Poster titled \textit{Mechanisms Underlying Retinoic Acid Deficient Cleft of the Secondary Palate}
\hfill
\DatestampY{2016}

\BigGap

\Entry
\textbf{FDI Annual World Dental Congress, Delhi}
\BulletItem
Poster titled \textit{Evaluation of Shear Bond Strength of Antibacterial property containing bonding agents}
\hfill
\DatestampY{2014}

\BigGap
\Entry
\textbf{Undergraduate Pedodontics Convention}
\BulletItem
Poster titled \textit{Mind the Grind} 
\hfill
\DatestampY{2014}
\newline
Highlighted the incidence, etiology and treatment of bruxism in special children

\Gap
\BulletItem
Poster titled \textit{Strap it early} 
\hfill
\DatestampY{2013}
\newline
Highlighted the importance of naso-alveolar molding in children with Cleft Lip and Palate

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% VOLUNTEERING ACTIVITY AND OTHER EXPERIENCES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Section
{VOLUNTEERING ACTIVITY \& OTHER EXPERIENCES}
{VOLUNTEERING ACTIVITY \& OTHER EXPERIENCES}
{PDF:VolunteeringActivity}

\Entry
\uLouisville

\Gap
\BulletItem
Student Assistant, Infection Control
\hfill
\DatestampYMD{2016}{09}{08} --
Present

\Gap
\BulletItem
Student Assistant, Kornhauser Library
\hfill
\DatestampYMD{2016}{05}{08} --
\DatestampYMD{2017}{02}{15}

\BigGap
\Entry
\ramachandra

\Gap
\BulletItem
Tobacco Cessation Camps
\hfill
\DatestampYMD{2015}{10}{08} 

\Gap
\BulletItem
Rotary Club of Madras Camps
\hfill
\DatestampYMD{2014}{07}{08} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Affiliations\newline
\& Activities}
{Professional Affiliations \& Activities}
{PDF:ProfessionalAffiliationsActivities}

\Entry
\href{http://www.aadronline.org/}
{\textbf{American Association for Dental Research}}
\newline
Student Research Group, Louisville Chapter

\Gap
\BulletItem
Vice-President
\hfill
\DatestampY{2017} --
\DatestampY{2018}

\Gap
\BulletItem
Treasurer
\hfill
\DatestampY{2016} --
\DatestampY{2017}

\BigGap
\Entry
\href{http://www.scadaresearch.org/us}
{\textbf{American Dental Association}}
\newline
Student Clinician (SCADA)

\BigGap
\Entry
\ramachandra

\Gap
\BulletItem
Dental Representative on University Student Council
\hfill
\DatestampY{2013} --
\DatestampY{2014}

\Gap
\BulletItem
Student Member of the Public Health Awareness Committee
\hfill
\DatestampY{2014} --
\DatestampY{2015}

% %%%%%%%%%%%%%%%%
% %% REFERENCES %%
% %%%%%%%%%%%%%%%%

\Section
 {References}
 {References}
 {PDF:References}

 \BulletItem
 \textbf{Dr. Vignesh Kailasam}
 \newline
 Professor, Dept. Of Orthodontics
 \newline
 Sri Ramachandra Dental College \& Hospital
 \newline
 \href{mailto:theorthodontist@gmail.com}
 {theorthodontist@gmail.com}
 \,\SubBulletSymbol\,
 +91\,9840237177

 \BigGap
 \BulletItem
 \textbf{Dr. Lisa Sandell}
 \newline
  Dept. of Oral Immunology \& Infectious Diseases
 \newline
 University of Louisville
 \newline
 501 S Preston St, Louisville, KY 40202
 \newline
 \href{mailto:lisa.sandell@louisville.edu}
 {lisa.sandell@louisville.edu}
 \SubBulletSymbol\,
+1\,502-852-7457

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %% THIS IS A SECTION WITH USAGE NOTES %%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% % Declare a new group to limit the scope of \color to this section.
% \begingroup
% \color{red}

% \Section
% {This is a\newline
% Section\newline
% With\newline
% Usage Notes}
% {This is a Section With Usage Notes (For PDF Bookmark)}
% {PDF:ThisIsASectionWithUsageNotes:ForPDFLink}

% \SubSection
% {This is a SubSection}
% {This is a SubSection (For PDF Bookmark)}
% {PDF:ThisIsASubSection:ForPDFLink}

% \Gap
% \BulletItem
% Use \CodeCommand{Section\{a\}\{b\}\{c\}} and
% \CodeCommand{SubSection\{a\}\{b\}\{c\}}
% to create sections and subsections, where
% \Code{a} is the heading displayed on the page,
% \Code{b} is the PDF bookmark heading, and
% \Code{c} is the internal PDF link (must be unique).
% Sections and subsections will appear in the PDF bookmarks.
% Note the CamelCase command names.

% \Gap
% \BulletItem
% Use
% \CodeCommand{Entry},
% \CodeCommand{BulletItem},
% \CodeCommand{SubBulletItem},
% \CodeCommand{Item},
% \CodeCommand{SubItem},
% \CodeCommand{NumberedItem},
% etc.,
% to create entries in the main body of the CV.

% \Gap
% \BulletItem
% Enclose entry details between
% \CodeCommand{begin\{Detail\}} and
% \CodeCommand{end\{Detail\}}
% so that they are typeset in a smaller font.
% \begin{Detail}
% \Item
% This is an example of entry detail text enclosed in a \Code{Detail} environment.
% \end{Detail}

% \Gap
% \BulletItem
% Use \CodeCommand{Gap} and \CodeCommand{BigGap} to insert vertical spaces between entries to improve layout.

% \BigGap
% \SubSection
% {This is Another SubSection}
% {This is Another Subsection (For PDF Bookmark)}
% {PDF:ThisIsAnotherSubSection:ForPDFLink}

% \Gap
% \Entry
% This is a plain \CodeCommand{Entry},
% followed by an \CodeCommand{hfill} and a date range
% \hfill
% \DatestampYM{2015}{10} --
% \DatestampYM{2015}{12}

% \Gap
% \BulletItem
% This is a \CodeCommand{BulletItem}.
% \Item
% This is an \CodeCommand{Item}, which has no bullet.
% Note the alignment with the \CodeCommand{BulletItem} above.

% \Gap
% \SubBulletItem
% This is a \CodeCommand{SubBulletItem}.
% \SubItem
% This is a \CodeCommand{SubItem}, which has no bullet.
% Note the alignment with the \CodeCommand{SubBulletItem} above.

% \Gap
% \NumberedItem{[42]}
% This is a \CodeCommand{NumberedItem}.
% Change the value of the macro \CodeCommand{MaxNumberedItem} to adjust the indentation width.

% \BigGap
% \SubSection
% {Line, Paragraph, and Page Breaks}
% {Line, Paragraph, and Page Breaks (For PDF Bookmark)}
% {PDF:LineParagraphAndPageBreaks:ForPDFLink}

% \Gap
% \BulletItem
% To create a new line within the same paragraph (i.e., preserving the same paragraph indentation), use \CodeCommand{newline} instead of \CodeCommand{\textbackslash};
% the latter will reset the paragraph indentation.

% \Gap
% \BulletItem
% To create a new paragraph, use \CodeCommand{par} or simply leave an empty line.
% Paragraph indentations (from
% \CodeCommand{Entry},
% \CodeCommand{BulletItem},
% \CodeCommand{SubBulletItem},
% \CodeCommand{Item},
% \CodeCommand{SubItem},
% \CodeCommand{NumberedItem},
% etc.) do not carry across different paragraphs.

% \Gap
% \BulletItem
% To create a new page, use \CodeCommand{newpage}.

% \BigGap
% \SubSection
% {Dates}
% {Dates (For PDF Bookmark)}
% {PDF:Dates:ForPDFLink}

% \Gap
% \BulletItem
% Use the following macros to specify and display dates consistently:
% \SubBulletItem
% \CodeCommand{DatestampYMD\{yyyy\}\{MM\}\{dd\}}
% (e.g., \CodeCommand{DatestampYMD\{2008\}\{01\}\{15\}})
% \SubBulletItem
% \CodeCommand{DatestampYM\{yyyy\}\{MM\}}
% (e.g., \CodeCommand{DatestampYM\{2008\}\{01\}})
% \SubBulletItem
% \CodeCommand{DatestampY\{yyyy\}}
% (e.g., \CodeCommand{DatestampY\{2008\}})

% \Gap
% \BulletItem
% Change the date format option passed to the document class to adjust how dates are displayed throughout the document:
% \SubBulletItem
% \Code{MMMyyyy} (``Jan~2008'')
% \SubBulletItem
% \Code{ddMMMyyyy} (``15~Jan~2008'')
% \SubBulletItem
% \Code{MMMMyyyy} (``January~2008'')
% \SubBulletItem
% \Code{ddMMMMyyyy} (``15~January~2008'')
% \SubBulletItem
% \Code{yyyyMMdd} (``2008-01-15'')
% \SubBulletItem
% \Code{yyyyMM} (``2008-01'')
% \SubBulletItem
% \Code{yyyy} (``2008'')

% \endgroup

\end{Body}

% %%%%%%%%%%%
% % CV NOTE %
% %%%%%%%%%%%

% \UseNoteFont%
% \null\hfill%
% [\textit{\CVNote}]

\end{document}
